---
title: ""
author: ""
date: ""
output: 
  html_document: 
    toc: true 
    toc_depth: 3
    toc_float: true
params:
  VSID: 0
---

```{r setup, include=FALSE,echo=FALSE,warning=FALSE}
# Setup knitr
knitr::opts_chunk$set(echo = TRUE)
# Load libraries
library(odbc)
library(tidyverse)
library(leaflet)
library(sf)
library(httr)
library(leaflet)
library(sf)
library(DT)


# Database connection
Connection = dbConnect(odbc(),Driver = "Sql Server",Server = "inp2300irmadb01\\ntwk", Database = "AKRO")

# Set the VSID to the VitalSign you want:
if(params$VSID == 0){
  #VSID = 18  #  ARCN   Brown Bears 
  VSID = 19  #  ARCN   Caribou 
  #VSID = 5  #  ARCN   Climate 
  # VSID = 7  #  ARCN   Coastal Shoreline Change 
  # VSID = 20  #  ARCN   Dall's Sheep 
  # VSID = 27  #  ARCN   Fire Extent and Severity 
  # VSID = 11  #  ARCN   Lagoon Communities and Ecosystems 
  # VSID = 12  #  ARCN   Lake Communities and Ecosystems 
  # VSID = 17  #  ARCN   Landbird Monitoring 
  # VSID = 21  #  ARCN   Moose 
  # VSID = 22  #  ARCN   Muskox 
  # VSID = 9  #  ARCN   Permafrost 
  # VSID = 133  #  ARCN   Shallow Lakes 
  # VSID = 13  #  ARCN   Stream Communities and Ecosystems 
  # VSID = 28  #  ARCN   Terrestrial Landscape Patterns and Dynamics 
  # VSID = 24  #  ARCN   Terrestrial Vegetation and Soils 
  # VSID = 81  #  ARCN   Western Yellow-billed Loons 
  # VSID = 40  #  CAKN   Air Quality 
  # VSID = 39  #  CAKN   Bald Eagle 
  # VSID = 134  #  CAKN   Caribou - DENA 
  # VSID = 49  #  CAKN   Caribou - WRST 
  # VSID = 36  #  CAKN   Climate 
  # VSID = 44  #  CAKN   Dall's Sheep 
  # VSID = 52  #  CAKN   Glaciers 
  # VSID = 54  #  CAKN   Golden Eagles 
  # VSID = 42  #  CAKN   Moose 
  # VSID = 38  #  CAKN   Passerines 
  # VSID = 31  #  CAKN   Peregrine Falcons 
  # VSID = 43  #  CAKN   Permafrost 
  # VSID = 51  #  CAKN   Plant Phenology 
  # VSID = 34  #  CAKN   Shallow Lakes 
  # VSID = 48  #  CAKN   Small Mammals 
  # VSID = 71  #  CAKN   Soundscape 
  # VSID = 72  #  CAKN   Streams and Rivers 
  # VSID = 37  #  CAKN   Vegetation Structure and Composition 
  # VSID = 45  #  CAKN   Wolves 
} else {
  VSID = params$VSID
}


# If you need an inventory of VSIDs:
# Get the vital signs
Sql = paste("SELECT Acronym,NetworkVSName,VSID FROM vwVitalSignOverview
  WHERE Status<>'Deferred' ORDER BY Acronym,NetworkVSName",sep="")
# Vital Sign overview data frame
VSInventory = dbGetQuery(Connection,Sql)
for(i in 1:nrow(VSInventory)){
  cat("VSID = ", VSInventory[i,'VSID']," # ",VSInventory[i,'Acronym']," ",VSInventory[i,'NetworkVSName'],"\n")
}


# Delete the existing html file
if (file.exists("VitalSignOverview.html")) {
  # Delete the file
  removed = file.remove("VitalSignOverview.html")
}



# Function to fix an SQL query by replacing every comma with a newline - makes sql more readable
FixSql = function(Sql) {
  FixedSql = gsub(",", "\n,", Sql)
  FixedSql = gsub(", ", ",", FixedSql)
  return(FixedSql)
}
```

```{r,label="Get the Vital Sign overview info", echo=FALSE,warning=FALSE}

# Build a query
Sql = paste("SELECT 
Acronym
,NetworkVSName AS VitalSign
,ProjectLeadLastname + ', ' + ProjectLeadFirstname as ProjectLeader
,'<a href=\"mailto:' + ProjectLeadEmail + '\">' + ProjectLeadEmail + '</a>' as Email
,ProjectLeadTelephone as Telephone
,Convert(varchar(8000),Overview) As Overview
,Status
,Convert(Date,ImplementationDate) as ImplementationDate
,Replace(FilesDirectory,'\','\\') as Directory
,Website
,Convert(varchar(1000),Address) as Address
,'[https://irma.nps.gov/DataStore/Reference/Profile/' + Convert(varchar(20),IRMAProjectReference) + '](https://irma.nps.gov/DataStore/Reference/Profile/' + Convert(varchar(20),IRMAProjectReference) + ')' as NPSDataStore
,ProjectLeadContactID
,IRMAProjectReference
,NetworkID,Network
,VSID
FROM vwVitalSignOverview
WHERE (VSID = ",VSID,")",sep="")

# Vital Sign overview data frame
vs = dbGetQuery(Connection,Sql)

# Fix the directory path so it will show OK in markdown
vs$Directory = gsub("\\\\", "\\\\\\\\", vs$Directory)

# Get the overview into a variable so it can be displayed in markdown
# Clean it so it displays in markdown better
#Overview = gsub("\r\n", "\n", vs$Overview) # iconv(vs$Overview, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "") 
Overview = iconv(vs$Overview, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "") 

```



# `r vs$VitalSign`
### Vital Sign Overview Report
*National Park Service, `r vs$Network` Inventory and Monitoring Program*

Scott D. Miller  
Information Technology Specialist
National Park Service, Arctic Inventory and Monitoring Network  
240 W. 5th Ave  
Anchorage, AK 99501  

`r format(Sys.Date(), "%B %d, %Y")`

# Introduction

This report presents a 'snapshot in time' overview of the Arctic Network's `r vs$VitalSign` monitoring program. Included are details on personnel, monitoring protocols, remeasurements and informational products.


# Vital Sign Overview

`r Overview`

## Map

```{r,echo=FALSE,warning=FALSE}

# Fix IRMA camelCase errors
capitalize_first_letter <- function(x) {
  str_replace_all(x, "\\b[a-z]", toupper)
}

# Define the URL
url = paste("https://irmaservices.nps.gov/datastore/v7/rest/Profile/",vs$IRMAProjectReference,"?format=json",sep="")

# Make the GET request
response <- GET(url)

# Extract the content as text
RESTContent <- content(response, "text")

# Parse the text into a JSON object
json <- jsonlite::fromJSON(RESTContent)

# Extract info from the REST query
Units = json$units
ProjectReferenceCode = json$referenceId
ProjectCitation = json$citation
ProjectLink = paste('<a href="https://irma.nps.gov/DataStore/Reference/Profile/',ProjectReferenceCode,'">',ProjectCitation,'</a>',sep='')
Visibility = json$visibility
Subjects = json$subjects
Keywords = json$keywords
Sensitivity = json$permissions$sensitivity
SensitivityDetail = json$permissions$sensitivityDetail
Quality = json$permissions$quality
UseConstraints = json$permissions$useConstraints
FileAccess = json$permissions$fileAccess
ReferenceOwners = json$permissions$referenceOwners
FileAccessUsers = json$permissions$usersWithFileAccess
ParksWKT = as.data.frame(json$boundingBoxes)
Products = as.data.frame(json$products)
# De-camelCase the column headings
colnames(Products) = sapply(colnames(Products), capitalize_first_letter)
Products$Product = paste('<a href="',Products$Citation,'"https://irma.nps.gov/DataStore/Reference/Profile/',ProjectReferenceCode,'">',Products$Citation,'<\\a>',sep='')

# Create a Product column with a link to the Data Store
Products = Products %>%
  mutate(Product = paste0('<a href="https://irma.nps.gov/DataStore/Reference/Profile/', Products$ReferenceId, '">', Products$Citation, '</a>'))

```

```{r,echo=FALSE,warning=FALSE}

# Sample data frame with WKT column
df <- data.frame(
  wkt = c(
    "POLYGON ((-122.4 37.8, -122.5 37.7, -122.3 37.6, -122.4 37.8))",
    "POLYGON ((-122.5 37.9, -122.6 37.8, -122.4 37.7, -122.5 37.9))"
  ),
  stringsAsFactors = FALSE
)

# Convert WKT to sf objects
#sf_data <- ParksWKT %>%  st_as_sf(wkt = "wkt", crs = 4326)
sf_data <- ParksWKT %>% st_as_sf(wkt = "wkt", crs = 4326)

# Create a leaflet map
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  addPolygons(data = sf_data, color = "blue", weight = 2, opacity = 0.5)


```

# Details

Details regarding the `r vs$VitalSign` monitoring program appear in Table 1.

```{r,label="Show the VS Details",echo=FALSE,tab.cap=paste("Table 1. ",vs$VitalSign," monitoring program details.",sep=""),warning=FALSE}

# Extract the vital sign details, transpose it tall and skinny
knitr::kable(t(vs %>% select(VitalSign
 ,ProjectLeader
 ,Email
,Telephone
,Status
,ImplementationDate
,Directory
,Website
,Address
,NPSDataStore,VSID)),escape = TRUE,na.rm=TRUE)

```

# Protocols 

Below are described the monitoring protocol(s) that have been implemented for the `r vs$VitalSign` monitoring program. Also shown are the schedule of deliverables to be fulfilled during each remeasurement cycle, and a list of completed remeasurements for the protocol.

```{r,label="VS Protocols",echo=FALSE,tab.cap=paste("Table 2. ",vs$VitalSign," monitoring protocol(s).",sep=""),warning=FALSE}

Sql = paste("SELECT [ProtocolTitle]
,[ProtocolCitation]
,[Version]
,[IRMAReferenceCode]
,[DateNarrativePublished]
,[DQSReferenceCode]
,[PIPSourceReferenceCode]
,[QAPReferenceCode]
--,[Notes]
--,[DocumentID]
--,[RecordInsertedDate]
--,[RecordInsertedBy]
--,[VSID]
,[ProtocolID]
  FROM [AKRO].[dbo].[tblVitalSignProtocols]
WHERE (VSID = ",VSID,") ORDER BY Version DESC",sep="")
protocols = dbGetQuery(Connection,Sql)
protocols$ProtocolCitation = iconv(protocols$ProtocolCitation, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")

```


```{r,label="output protocols",results='asis',echo=FALSE,warning=FALSE}
for(i in 1:nrow(protocols)){
  Title = protocols[i,'ProtocolTitle']
  Citation = protocols[i,'ProtocolCitation']
  ProtocolID = protocols[i,"ProtocolID"]
  RefCode = protocols[i,"IRMAReferenceCode"]
  ProtocolReference = paste("[",Citation,"](https://irma.nps.gov/DataStore/Reference/Profile/",RefCode,") \n",sep="")
  cat("## ",Citation,"  \n")
 
  print(knitr::kable(t(protocols)))
  
  cat("### Deliverables Schedule  \n")
  
  Sql = paste("SELECT  [DeliverableIdentifier]
,[Deliverable]
--,[SOP]
--,[SOPVersion]
--,[Format]
--,[Description]
,[Schedule]
,[Responsibility],ProtocolID
  FROM [AKRO].[dbo].[tblProtocolDeliverables]
WHERE ProtocolID=",ProtocolID," 
ORDER BY DeliverableIdentifier",sep="")

  ds = dbGetQuery(Connection,Sql)
    cat("This protocol describes the collection, delivery and management of ",nrow(ds)," deliverables.  \n\n",ProtocolReference,"  \n  ")
    cat("  \n\n")
    print(knitr::kable(ds %>% filter(ProtocolID == protocols$ProtocolID)))
    cat("  \n\n")
    
 #  cat("### Remeasurements  \n  ")
 #  Sql = paste("SELECT 
 #      -- [Description]
 #      --,[BeginDate]
 #      --,[EndDate]
 #      isnull('<a href=https://irma.nps.gov/DataStore/Reference/Profile/'+ Convert(Varchar(20),[DeliverablesIRMAReferenceCode]) + '>' + Description + '</a>',Description) as Deliverables
 #      ,[DeliverablesIRMAReferenceCode]
 #      ,'<a href=https://irma.nps.gov/DataStore/Reference/Profile/'+ Convert(Varchar(20),[ReportIRMAReferenceCode]) + '>'+ Convert(Varchar(20),[ReportIRMAReferenceCode]) + '</a>' as Report
 #      
 #      --,[Notes]
 #      --,[RemeasurementAbstract]
 #      --,[ProtocolID]
 #      --,[RecordInsertedDate]
 #      --,[RecordInsertedBy]
 #      --,[RemeasurementID]
 #  FROM [AKRO].[dbo].[tblProtocolRemeasurements]
 # WHERE ProtocolID=",ProtocolID,"
 # ORDER BY Description DESC",sep="")
 #    rm = dbGetQuery(Connection,Sql)
 #    
 #    cat("  \n")
 #    cat("This protocol has been used during ",nrow(rm)," remeasurements:\n\n",Citation,"  \n")
 #    cat("  \n")
 #    print(knitr::kable(rm,na.rm=TRUE))
 #    #print(datatable(rm, options = list(pageLength = 100, autoWidth = TRUE),escape=FALSE))
 #    #%>% mutate(Product = paste0('<a href="https://irma.nps.gov/DataStore/Reference/Profile/', Products$ReferenceId, '">', Products$Citation, '</a>'))
 #    cat("  \n")

}

```

# IRMA Project Reference Overview

The section below shows basic information about the Vital Sign's Project Reference in the NPS Data Store, including relevant Parks, reports, journal articles and datasets.

`r ProjectLink`



## Products



```{r,echo=FALSE,warning=FALSE}
Prods = Products %>% select(Product,ReferenceType,Visibility,FileCount,ReferenceId) %>% arrange(Product)
# Render the data table with sorting and filtering options 
 datatable(Prods, options = list(pageLength = 100, autoWidth = TRUE),escape=FALSE)
# #write.table(Products %>% select(Title,ReferenceId),paste("C:/Temp/z",vs$VitalSign," Products.csv",sep=""),row.names = FALSE,na="",quote = FALSE)
# 
# Sql = Products %>% mutate(`begin transaction -- commit rollback` = paste("INSERT INTO tblProtocolRemeasurements(ProtocolID,Description,StartDate,EndDate)VALUES(",vs$VSID,",'",Products$Title,"',","@StartDate,@EndDate)",sep="")) %>% 
#   select(`begin transaction -- commit rollback`) %>% arrange(Products$Title)
# for(i in 1:nrow(Sql)){
#   cat(Sql$`begin transaction -- commit rollback`,"  \n\n","\n")
# }
```



```{r,label="Write the report to the survey directory", echo=FALSE,warning=FALSE}

# This template will output to an html file named MooseSurveyReport.htms
# Rename it and copy it to the survey directory if it exists
# Otherwise rename it in the current directory
From = "VitalSignOverview.html"

# Set up the source file title
ReportTitle = paste(vs$Acronym," ",vs$VitalSign," Summary.html",sep="")

# Check if the survey directory exists
# Set up a destination file path for the file copy operation
# if (dir.exists(DashboardDF$DataResourcesDirectory)) {
#   To=paste(DashboardDF$DataResourcesDirectory,"/",ReportTitle,sep="")
# } else {
#   To=ReportTitle
# }
To=ReportTitle

# # Try to copy the file to the destination
# tryCatch({
#   #printed = file.copy(From, To, overwrite = TRUE)
#   #message(paste("Report ",From," generated and and copied to ",To,sep=""))
# }, error = function(e) {
#   
#   # An error happened
#   message("Error: ", e$message)
#   
# })


```




















